Ripple Protocol Consensus Algorithm Review

### 2015-05-12 paper.tex
fix typos

We do \emph{not} try to determine the monetary impact of the attack, because we
are unable to predict how the Ripple network will be used. For instance, while
a double-spend attack may have the same basic impact on a $\$100/\text{day}$
small business as it would on a $\$1,000,000,000/\text{day}$ multinational, the
latter could lose orders of magnitude more money for what it at a technical
level basically the same attack. A closely issue with attempting to predict
monetary losses is that at some point losses can be sufficiently high that they
create situations where social consensus can decide that the losses simply must
be reversed. For instance, Vericoin community chose to do a hard-fork of their
alt-currency to undo the impact of a major theft.\cite{coindesk-vericoin}

@@

The attacker steals illegitimate control of the secret keys used by validators,
particularly the validators in the default UNL. The theft may happen via an
exploit, backdoor, compromised hosting company, etc. While not useful for the
attacker in of itself, the stolen keys can be used for further attacks such as
DoS or a simulated ledger attack.

@@

The transaction flood results in the pseudoanonymous ``DarkWeb'' validators
quitting - the Tor network is too slow to handle the load, and they worry
they're real identities will be discovered if they move their validator nodes
to clearnet hosting.

@@

What has actually happened is Russian cyberwarfare experts created a fake
consensus using stolen Swiss and French private keys. Russia of course
officially signed this fake consensus, as well as the real consensus, taking
the position this was an above-the-board court ordered operation; China also
signed, but doesn't officially say why. The wealthy Chinese investor
conveniently claims to have suddenly found out about the ``fake'' oil importer
and on the real Ripple ledger has the funds frozen by the Chinese bank backing
them - not a big deal with the money still sitting in the original account he
deposited it too, still under Chinese jurisdiction.

>>>>

We do \emph{not} try to determine the monetary impact of the attack, because we
are unable to predict how the Ripple network will be used. For instance, while
a double-spend attack may have the same basic impact on a $\$100/\text{day}$
small business as it would on a $\$1,000,000,000/\text{day}$ multinational, the
latter could lose orders of magnitude more money for what is at a technical
level basically the same attack. A closely related issue with attempting to predict
monetary losses is that at some point losses can be sufficiently high that they
create situations where social consensus can decide that the losses simply must
be reversed. For instance, Vericoin community chose to do a hard-fork of their
alt-currency to undo the impact of a major theft.\cite{coindesk-vericoin}

@@

The attacker steals illegitimate control of the secret keys used by validators,
particularly the validators in the default UNL. The theft may happen via an
exploit, backdoor, compromised hosting company, etc. While not useful for the
attacker in and of itself, the stolen keys can be used for further attacks such as
DoS or a simulated ledger attack.

@@

The transaction flood results in the pseudoanonymous ``DarkWeb'' validators
quitting - the Tor network is too slow to handle the load, and they worry
their real identities will be discovered if they move their validator nodes
to clearnet hosting.

@@

What has actually happened is Russian cyberwarfare experts created a fake
consensus using stolen Swiss and French private keys. Russia of course
officially signed this fake consensus, as well as the real consensus, taking
the position this was an above-the-board court ordered operation; China also
signed, but doesn't officially say why. The wealthy Chinese investor
conveniently claims to have suddenly found out about the ``fake'' oil importer
and on the real Ripple ledger has the funds frozen by the Chinese bank backing
them - not a big deal with the money still sitting in the original account he
deposited it to, still under Chinese jurisdiction.
